---
title: "GeoLift Vignette Walkthrough"
date: 2022-06-13
output: html_notebook
---

## Overview

Walking through the vignette for [GeoLift](https://github.com/facebookincubator/GeoLift/blob/main/vignettes/GeoLift_Walkthrough.md).
I made some notes while working through it about things to look into later.

## Stuff

```{r}
library("GeoLift")
```

```{r}
data("GeoLift_PreTest")
```

- location
- date
- Y (convertsions/KPI in day/location)

```{r}
GeoLift_PreTest
```

`GeoDataRead()`: input is a data frame, returns a data frame. Purpose
is to format data correctly.

**TODO:** How are the covariates in `X` used? 

```{r}
GeoTestData_PreTest <- GeoDataRead(data = GeoLift_PreTest,
                                   date_id = "date",
                                   location_id = "location",
                                   Y_id = "Y",
                                   X = c(), #empty list as we have no covariates
                                   format = "yyyy-mm-dd",
                                   summary = TRUE)
```

The `GeoPlot()` 

- trend
- contribution per location
- detect any data anomalies before moving on to the data analysis.

```{r}
GeoPlot(GeoTestData_PreTest,
        Y_id = "Y",
        time_id = "time",
        location_id = "location")
```
## Power

- The optimal number of test locations.
- Best test duration.
- Select the ideal test and control markets.
- Get a good estimate of the budget needed to run the test.
- Determine which is the Minimum Detectable Effect to obtain significant results.
- Align expectations. 

Notes: 

- assumes homogenous treatment
- the way that periods are constructed means that different periods of time are included
- lookbacks are highly correlated because they are only incremented one time period.
- Focuses on ATT. However, for MMM need ATE. Includes `Correlations` to get those.
- Extremely Specialized to marketing / ads experiments. 
- Does not do multiple responses (augsynth handles that)
- Could be extended to take MMM existing estimates of uncertainty and apply them to the choice of locations.
- TODO: look more at Robyn MMM models and how they interact with geo-spatial experiments.
- TODO: look at missing data handling. This is not handled within GeoLift. Could we match on factors instead of Y's?. 
- I like how it uses the budget constraints

Notes on the parameters of `Geo

- `data` A data frame containing the historical conversions by geographic unit.
- `treatment_periods`: Need to specify several number of time period to check
- `N`: Need to specify the number of of markets to calculate power for
- `X` names of additional covariates
- `Y_id`, `location_id`, `time_id`: name of outcome, location, time features in `data`
- `effect_size`: Effect sizes to simulate (these are relative percent sizes). Default is `seq(0, 0.25, 0.05)`
- `lookback_window`: Lookback windows - simply moves the tests back 1 week.
- `include_markets`: Lists of markets that must be in the test group
- `exclude_markets`: Lists of markets that cannot be in the test group
- `holdout`: The smallest desirable holdout, the largest desirable holdout. This is the share of markets that won't see an ad campaign.
- `cpic`: Value indicating the Cost Per Incremental Conversion. CPIC = 1 if no info.
- `budget`: Max allowable budget
- `alpha`: Significance level. Uses 90% by default. By default alpha = 0.1 which is equivalent to a 90% confidence level.
- `model`: Allows a model to augment Augmented Synthetic Control method.
- `fixed_effects`: Default is `TRUE`. Best if stable.
- `Correlations`: Correlations = FALSE.
- `print`: Flag to print the top results
- `parallel`: 
- `parallel_setup`
- `side_of_test`: One or two-sided test. Default is two-sided. Why? Shouldn't it be one-sided? 

```{r market_selections}
MarketSelections <- GeoLiftMarketSelection(data = GeoTestData_PreTest,
                                          treatment_periods = c(10,15),
                                          N = c(2,3,4,5),
                                          Y_id = "Y",
                                          location_id = "location",
                                          time_id = "time",
                                          effect_size = seq(-0.25, 0.25, 0.05),
                                          lookback_window = 1, 
                                          include_markets = c("chicago"),
                                          exclude_markets = c("honolulu"),
                                          cpic = 7.50,
                                          budget = 100000,
                                          alpha = 0.1,
                                          Correlations = TRUE,
                                          fixed_effects = TRUE,
                                          side_of_test = "one_sided")

```

- What does "well-powered" mean? Based on the plots it uses the 80% power default.
- What are these sorted by? 
- `ScaledL2Imbalance` is difficult to interpret
- `abs_lift_in_zero`
- what is correlation in relation to?
- how does it rank them? "Ranking variable that summarizes the `EffectSize`, Power, `AvgScaledL2Imbalance`, `Average_MDE`, and `abs_lift_in_zero` to help you select the best combination of test markets. The ranking variable allows for ties? 

  - See [here](https://github.com/facebookincubator/GeoLift/blob/b9ded752094b28cec236f4d0e18ca93e2f61c7f5/R/pre_test_power.R#L767) The rank is the average of the ranks of 
  
    - MDE (abs(effect size))
    - p-Value
    - Abs. Effect size in 0 (detected lift - effect)

- What is "deterministic"? See [here](https://github.com/facebookincubator/GeoLift/blob/b9ded752094b28cec236f4d0e18ca93e2f61c7f5/R/pre_test_power.R#L120)

How does it do market matching? It uses the [MarketMatching](https://cran.r-project.org/web/packages/MarketMatching/vignettes/MarketMatching-Vignette.html) package

```
    mm <- MarketMatching::best_matches(
      data = data,
      id_variable = "location",
      date_variable = "astime",
      matching_variable = "Y",
      parallel = FALSE,
      warping_limit = 1,
      dtw_emphasis = dtw,
      start_match_period = min(data$astime),
      end_match_period = max(data$astime),
      matches = length(unique(data$location)) - 1
    )
```

Notes:

- MarketMatching does suggested splits. This does not do that.
- Matching markets using dynamic time warping doesn't make sense if the synthetic control is matching on linear covariates
  (though augsynth is better).


```{r}
library("ggplot2")
market_id = 3
market_row <- MarketSelections$BestMarkets %>% dplyr::filter(ID == market_id)
treatment_locations <- stringr::str_split(market_row$location, ", ")[[1]]
treatment_duration <- market_row$duration
lookback_window <- 10

power_data <- GeoLiftPower(
  data = GeoTestData_PreTest,
  locations = treatment_locations,
  effect_size = seq(-0.15, 0.15, 0.01),
  lookback_window = lookback_window,
  treatment_periods = treatment_duration,
  cpic = 7.5,
  side_of_test = "one_sided"
)
#> Setting up cluster.
#> Importing functions into cluster.

plot(power_data, show_mde = TRUE, smoothed_values = FALSE, breaks_x_axis = 5) +
    labs(caption = unique(power_data$location))
```

Notes:

- Why is power asymmetric for a specific choice? 

  - Periods are fixed. I thought it had to do with the weird things that happen with differing lookback periods.
  - Is it just randomness? 
  
- Also, power is literally undefined at 0 since $H_0 = H_a$ at that point. Alternatively, it is equivalent to $\alpha$. 
  If $\alpha = 0.1$, then there should be 10\% significant simulations.
  

```{r}
plot(MarketSelections, market_ID = 3, print_summary = TRUE)
```


Notes:

- For comparisons it would be better to show a plot of differences as well as levels.
- Idea: Could we calculate a value at risk? 
- Test + Holdout seems to not equal 100% because of 0 weights in SCM

How are p-values constructed? They use `augsynth::compute_permute_pval`.

See https://github.com/facebookincubator/GeoLift/blob/main/R/pre_test_power.R#L306

- Avg. treatment conversions = actual Y's for treated averaged by day/unit.
- Incremental conversions = Difference with predicted control conversions.
- ATT estimator: Avg. incremental conversions / time-periods
- lift estimator: Avg incremental conversions / sum(avg. predicted control conversions)
 
Something that's bothering me. The response variable is always the level number of conversions. I think they should match on log levels or similar.

Problem in code: They `cbind` a matrix!! https://github.com/facebookincubator/GeoLift/blob/main/R/pre_test_power.R#L501



## Example: Analyzing the test results

```{r}
data(GeoLift_Test)
```

```{r}
GeoTestData_Test <- GeoDataRead(data = GeoLift_Test,
                                date_id = "date",
                                location_id = "location",
                                Y_id = "Y",
                                X = c(), #empty list as we have no covariates
                                format = "yyyy-mm-dd",
                                summary = TRUE)
#> ##################################
#> #####       Summary       #####
#> ##################################
#> 
#> * Raw Number of Locations: 40
#> * Time Periods: 105
#> * Final Number of Locations (Complete): 40
head(GeoTestData_Test)
#>   location time    Y
#> 1  atlanta    1 3384
#> 2  atlanta    2 3904
#> 3  atlanta    3 5734
#> 4  atlanta    4 4311
#> 5  atlanta    5 3686
#> 6  atlanta    6 3374
```


```{r}
GeoPlot(GeoTestData_Test,
        Y_id = "Y",
        time_id = "time",
        location_id = "location",
        treatment_start = 91)
```

TODO:

- We need to automate the search for outliers


```{r}
GeoTest <- GeoLift(Y_id = "Y",
                   data = GeoTestData_Test,
                   locations = c("chicago", "portland"),
                   treatment_start_time = 91,
                   treatment_end_time = 105)
#> Running model with no prognostic function.
GeoTest
```

Notes:

- There really should be no two-sided tests. They never make sense.


The L2 Imbalance is really a bad metric for eval. It is hard to understand and is too statistical. 
It should be translated into the scale of the response metric to be useful.

> A small L2 Imbalance score means that our model did a great job replicating our test locations while a large one would indicate a poor fit. However, the L2 Imabalnce metric is scale-dependent, meaning that it can’t be compared between models with different KPIs or number of testing periods. For instance, the L2 Imbalance of a model run on grams of units sold will be significantly larger than a model ran for tons of product sold even if they represent the same basic underlying metric


```{r}
plot(GeoTest, type = "Lift")
```

```{r}
plot(GeoTest, type = "ATT")
```

GeoLift can automatically select between models:

1. Synthetic control only
2. Ridge augmented
3. Gsynth augmented

These should always be selected automatically.

```{r}
GeoTestBest <- GeoLift(Y_id = "Y",
                       data = GeoTestData_Test,
                       locations = c("chicago", "portland"),
                       treatment_start_time = 91,
                       treatment_end_time = 105,
                       model = "best")
```

